   % /--------------------------------------------\
   % | API-Dokumentation für einige Java-Packages |
   % |    (genaueres siehe doku-main.tex).        |
   % | LaTeX-Ausgabe erstellt von 'ltxdoclet'.    |
   % | Dieses Programm stammt von Paul Ebermann.  |
   % \--------------------------------------------/

   % Api-Dokumentation für Klasse ontologyFramework.OFProcedureManagment.OFSchedulingBuilder (noch nicht fertig). 
\section[OFSchedulingBuilder]{Klasse \ltdHypertarget{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder-class}{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder}}\label{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder-class}
\subsection{Übersicht}
This class is design to initialize (build) a Quartz scheduler
 object with respect to the ontology into the framework. It
 will build an HashMap between the name of an ontological individual 
 and a \noprint{@link:org.quartz.Scheduler}\texttt{Scheduler} which is given by:
 \verb!sch = new StdSchedulerFactory( propertyPath).getScheduler();!.
 This map will be available than into the static map manager: 
 \noprint{@link:OFBuildedListInvoker}\texttt{\hyperlink{ontologyFramework.OFRunning.OFInvokingManager.OFBuildedListInvoker-class}{OFBuildedListInvoker}}.
 
 By definition the individual which reflect the building mechanism 
 used in this implementation is:
 {\ttfamily
\mbox{ }	\verb!B_SchedulerBuilding € OFBuilder !\mbox{ }\mbox{ }\mbox{}\newline
\mbox{ }		\verb!hasTypeName "ontologyFramework.OFProcedureManagment.OFSchedulingBuilder"^^string!\mbox{}\newline
\mbox{ }		\verb!buildList "SchedulerList"^^string!\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{}\newline
\mbox{ }		\verb!hasTypeKeyWord "QuartzScheduler hasQuartzSchedulerProperty"^^string!\mbox{ }\mbox{}\newline
\mbox{ }}

 Where the first key word is relate to the name of the ontological
 class to looking for scheduling individuals. While the second is
 the name of Object Property which link an individual to its
 .properties file.  
 This basically means that to define an individual which will be 
 one to one relate with a Quartz scheduler object just create it as:
 {\ttfamily
\mbox{ }	\verb!S_Scheduler1 € QuartzScheduler !\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{ }\mbox{}\newline
\mbox{ }		\verb!hasQuartzSchedulerProperty exactly 1 FileInd!\mbox{}\newline
\mbox{ }			where:\verb!FileInd € File!\mbox{}\newline
\mbox{ }					\verb!KeyFileInd hasTypeFile "/src/sempleSch.property"^^string!\mbox{ }\mbox{}\newline
\mbox{ }}

\begin{description}
\item[@author] 
Buoncomapgni Luca
\item[@version] 
1.0
\end{description}
\subsection{Inhaltsverzeichnis}
\subsection{Konstruktoren}
\begin{description}
\item[{\ltdHypertarget{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder()}{OFSchedulingBuilder}\label{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder()}}]
~ 
\end{description}
\subsection{Methoden}
\begin{description}
\item[{\ltdHypertarget{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder.buildInfo(java.lang.String[],ontologyFramework.OFContextManagement.OWLReferences,ontologyFramework.OFRunning.OFInvokingManager.OFBuildedListInvoker)}{buildInfo}\label{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder.buildInfo(java.lang.String[],ontologyFramework.OFContextManagement.OWLReferences,ontologyFramework.OFRunning.OFInvokingManager.OFBuildedListInvoker)}}]
~ 
\item[{\ltdHypertarget{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder.getInitialisedClasses()}{getInitialisedClasses}\label{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder.getInitialisedClasses()}}]
~ 
\item[{\ltdHypertarget{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder.shotDownAllScheduler()}{shotDownAllScheduler}\label{ontologyFramework.OFProcedureManagment.OFSchedulingBuilder.shotDownAllScheduler()}}]
~ shouts down (\verb!scheduler.shoutdown()!) all the scheduler builded from
 this class during previous building time.
\end{description}
